```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# problem
you want to append a data base inside a shapefile, using different reference cagories.

# solution 
the package base has the ``merge`` function that can make join of two data frames 

```{r merge}
library(base)
cities <- readOGR( ".", "xxxx" )
renda <- read.csv( "renda_distrito.R", header = TRUE )
str( cities, 2 )
str(renda)
cities.renda <- merge( by = "nombre.distrito", cities@data$distrito, renda )
str( cities.renda )
cities@data$renda <- cities.renda$x
```

#Discusion 

To know the structure of shapefile and of a variavel used is important for the join. we need have a reference variavel with the categories of reference for could make the join for this do you need select a variavel that has the diferents categories of shapefile as the other file. After applied a funtion ``merge``, a new dataframe is create with two variavels, the firs variavel are references categories and the second .........

# see also















