```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to read a shapefile.

# Solution
The ``rgdal`` package has the function ``readOGR()`` to read shapefiles:
```{r readOGR}
library(rgdal)
cities <- readOGR('../../Data', 'cities')
```
The ``maptools`` package also has functions to read shapefiles:
```{r readShape}
library(maptools)
cities <- readShapeSpatial('../../Data/cities')
```


# Discussion
The Esri [shapefile](http://en.wikipedia.org/wiki/Shapefile), or simply a shapefile, is a popular geospatial vector data format for storing geometric location and associated attribute information. A shapefile is a set of files. Three individual files are mandatory to store the core data that comprise a shapefile: .shp, .shx, and .dbf. There are further optional files which store primarily index data to improve performance. All files should be located in the same folder.  

When using ``readOGR()`` to read ``cities.shp`` located at ``~/Data (windows: C:/Data)``, define the ``dsn`` argument as the path and the ``layer`` argument as the name of the file without extension. For example: ``readOGR('~/Data', "cities")``. If the shapefile is in the current working directory, an equivalent function call is: ``readOGR('.', "cities")``. See ``?readOGR`` for a detailed description of available arguments.  

With ``readShapeSpatial()``, use ``readShapeSpatial('~/Data/cities')`` to read ``cities.shp`` located at ``~/Data (windows: C:/Data)``. If the shapefile is in the current working directory, an equivalent function call is: ``readShapeSpatial('cities')``. The maptools package also has specific functions for each vector data type: ``readShapePoints()``, ``readShapePoly()`` and ``readShapeLines()``. ``readShapeSpatial()`` can be used instead of the previous three functions. See ``?readShapeSpatial`` for a detailed description of available arguments.  

# See also
XXX Draft XXX  
Classes and methods section for a description of the structure of created objects (in this case ``cities``).   













