```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to display the `SpatialPoints` and `SpatialPointsDataFrame` classes structure and to build objects of theses classes.

# Solution
`SpatialPoints` and `SpatialPointsDataFrame` classes structure.
```{r readOGR}
library(sp)
getClass('SpatialPoints')
getClass('SpatialPointsDataFrame')
```

Building a `SpatialPoints` object.
```{r sp}
# Draw a random sample of points.
pts <- matrix(c(sample(3:10, 10, r = T),
                sample(70:100, 10, r = T)),
              nc = 2)

crs <- CRS(projargs = as.character(NA))
sp.pt <- SpatialPoints(pts, crs)

str(sp.pt, 2)
summary(sp.pt)

# bbox is created from pts.
bbox(sp.pt)

# Access the first 3 coordinates
coordinates(sp.pt[1:3, ])
```

Building a `SpatialPointsDataFrame` object.
```{r spdf}
# First option.
df <- data.frame(
  total.cases = sample(100:200, 10, r = T),
  fatal.cases = sample(10:50, 10, r = T))

sp.ptdf <- SpatialPointsDataFrame(pts, df,
                                  proj = crs)

# Second option.
sp.ptdf2 <- data.frame(total.cases = df[ , 1],
                       fatal.cases = df[ , 2],
                       long = pts[ , 1],
                       lat = pts[ , 2])
coordinates(sp.ptdf2) <- 3:4
proj4string(sp.ptdf2) <- crs
```

# Discussion
Note that the `SpatialPoints` class extends the `Spatial` class adding the `coords` slot. `coords` slot is a `matrix` containing the points coordinates. On the other hand, `SpatialPointsDataFrame` extends `SpatialPoints` adding the `data` and `coords.nrs` slots. `data` slot is a `data.frame` with features or attributes of the points. Each row is associated with a point. There are different ways to create a `SpatialPointsDataFrame`. When the `data.frame` with points features also has the points coordinates, the `coords` slot can be created from that `data.frame`. When this procedure is used, the columns in `data` slot with the coordinates are moved to the `coords` slot. `coords.nrs` indicates the index of that columns in the original `data.frame`.  

There are at least to options to create a `SpatialPointsDataFrame`. Using the first option, the row names in the `matrix` an the row names in the `data.frame` must be the same to match both sources of data. If the row names are not in the same order in both objects, the `data.frame` is re-ordered  to match the row names in the  `matrix`. This is useful because the coordinates and the features might be obtained from different sources and it often happens that the features associated with a point are not in the same row as the point.  

The second option produces a result equivalent to that of the first one. The main difference is in the `coords.nrs` slot, which in the second option indicates the columns in the original `data.frame` that contained the coordinates. The row names of the `coords` and `bbox` slots are set as the names of the columns with the coordinates in the original `data.frame`.



# See also































