```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to display the structure of classes used to represent lines as well as the structure of an object of class `SpatialLinesDataFrame`.

# Solution
1. Use the `getClass` function to display the definition of classes.
```{r readOGR}
library(sp)
getClass('Line')
getClass('Lines')
getClass('SpatialLines')
getClass('SpatialLinesDataFrame')
```

2. Import a shapefile with data represented by lines using the `readOGR` function from the `rgdal` package and then inspect the specific slots of a `SpatialLinesDataFrame` object:
```{r SpatialLinesDataFrame}
library(rgdal)
# Import the shapefile.
fylk <- readOGR('../../Data', 'fylk_val')
  
# Display the general structure and the second object of the "lines" slot.
str(fylk, 2)
str(fylk@lines[[2]])
fylk@lines[[2]]@Lines
```

# Discussion
Representation of lines in the `sp` package follows a hierarchical approach with a more complex structure in comparison with the representation of points.  
 
The `Line` class has two slots: `coords` and `ID`. The `coords` slot, which is a `matrix` to store point coordinates. It is the interpolation between these points (stright lines beteewn two succesive points) that represents lines. The `ID` slot has an identifying character string.

The `Lines` class has the `Lines` slot, which is a `list` of `Line` objects.  

Note that `SpatialLines` class extends the `Spatial` class adding the `lines` slot, which is a `List` of `Lines` objects. On the other hand, `SpatialLinesDataFrame` extends `SpatialLines` adding the `data` slot, a `data.frame` with features or attributes of the lines. Each row is associated with a line. The `ID` slot is used to match `Liness` objects stored in the `lines` slot, with observations in the `data` slot.

# See also
