```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to build a `SpatialPointsDataFrame` object, inspect their structure.

# Solution
First option: use 1: a `matrix` of coordinates with an integer sequence as row names; 2: a `CRS` object; and 3: a `data.frame` with row names that associate the features in the `data.frame` with the coordinates in the `matrix`; as arguments for the `SpatialPointsDataFrame` function.  
Second option: use a `data.frame` with both the coordinates and the features as the argument for the `coordinate`function an assign to it the index (or names) of the columns containing the coordinates. Use the same `data.frame` as the argument for the `proj4string` function and assing to it an `CRS`oject.
```{r readOGR}
library(sp)
## First option
# Draw a random sample of points.
pts <- matrix(c(sample(3:10, 10, r = T),
                sample(70:100, 10, r = T)),
              nc = 2,
              dimnames = list(1:10, NULL))

crs <- CRS(projargs = as.character(NA))

# Draw a random sample of features
df <- data.frame(
  total.cases = sample(100:200, 10, r = T),
  fatal.cases = sample(10:50, 10, r = T))

sp.ptdf <- SpatialPointsDataFrame(pts, df,
                                  proj = crs)
str(sp.ptdf, 2)
summary(sp.ptdf)

## Second option.
sp.ptdf2 <- data.frame(total.cases = df[ , 1],
                       fatal.cases = df[ , 2],
                       long = pts[ , 1],
                       lat = pts[ , 2])
coordinates(sp.ptdf2) <- 3:4
proj4string(sp.ptdf2) <- crs
str(sp.ptdf2, 2)

## Access the first 3 lines of the data.frame
sp.ptdf2@data[1:3, ]
```

# Discussion
Using the first option, the row names in the `matrix` an the row names in the `data.frame` must be the same to match both sources of data. If the row names are not in the same order in both objects, the `data.frame` is re-ordered  to match the row names in the  `matrix`. This is useful because the coordinates and the features might be obtained from different sources and it often happens that the features associated with a point are not in the same row as the point.  
The second option produces a result equivalent to that of the first one. The main difference is in the `coords.nrs` slot, which in the second option indicates the columns in the original `data.frame` that contained the coordinates. The row names of the `coords` and `bbox` slots are set as the names of the columns with the coordinates in the original `data.frame`.

# See also


















































