```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to build a simple `Spatial` object and acces their slots.

# Solution
Create a `matrix` with the requirements of a `bbox` and a `CRS` object. Use these objects as arguments for `Spatial` function:
```{r readOGR}
library(sp)
box <- matrix(c(4, 70, 5, 80), ncol = 2,
              dimn = list(NULL, c('min', 'max')))
crs <- CRS(projargs = as.character(NA))
(sp.object <- Spatial(bbox = box,
                      proj4string = crs))

# The maximal level of nesting that str
# displays can be controlled
str(sp.object, 2)

summary(sp.object)

# Access and display the slots separately.
bbox(sp.object)
proj4string(sp.object)
```

# Discussion
Vector and raster data are often read from files and the reading process defines the `bbox` and `proj4string` slots. Remember that `slot(sp.object, 'bbox')` and `sp.object@bbox` are valid methos to access the `bbox`. The same is thrue for other slots (i.e. `proj4string`).  
`str` and `summary` are conveninet functions to inspect the structure of `Spatial` objects. Controling the maximal level of nesting displayed by the `str` is a useful option specially for objects with slots that have many levels of nesting or objects with many elemnts. Compare the result of  `str(sp.object, 2)` and `str(sp.object)`.


# See also



















































