```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to inspect the `Spatial` class definition.

# Solution
The `Spatial` class is provided by the sp package and the definition is displayed using the `getClass` function:
```{r readOGR}
library(sp)
getClass('Spatial')
```
The class of bbox and proj4string slots can also be displayed:
```{r readShape}
getClass('CRS')
```

# Discussion
`Spatial` objects has two slots. The `bbox` (bounding box) slot is a `matrix` defining the x-axis or eastings (first row) and y-axis or northings (second row) with numbers representing cooordinates. The `bbox` must have `c('min', 'max')` as column names. The `proj4string` slot is a string of class `CRS` defining the coordinate reference system. By default, the `proj4string` slot is defined as `NA`.

Displaying the `Spatial`class definition also shows the known sublcasses which inherit the `bbox` and `proj4string` slots. As you might expect, these subclasses are ingredients for recepies of subsequent sections.

# See also
































