```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to identify the CRS of a spatial object.

# Solution
```{r}
library(rgdal)

# Read two shape files.
muns <- readOGR('../../Data/municipios_IBGE', 'Municipios_IBGE')
fylk <- readOGR('../../Data', 'fylk_val')

# Print the CRS.
proj4string(muns)
proj4string(fylk)

# Check if the CRS is projected.
is.projected(muns)
is.projected(fylk)
```

# Discusion
The `proj4string` function print thes CRS of a spatial object, which is represented as a set of "tag=value" pairs or [parameters](https://trac.osgeo.org/proj/wiki/GenParms). For the `muns` object, it can be seen that the projection is "longlat" - meaning that the CRS is geographical or unprojected - and the ellipsoid is GRS80. For the `fylk` object, more parameters define the CRS; the projection is UTM, the UTM zone is 33, the datum is WGS84, the unit of measurment is the meter and the ellipsoid is WGS84. The "+towgs84" tag shows the translation (3 values) or the translation + rotation + scaling (7 values) needed to transform the datum to WGS84.


