```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Problem
You want to set the CRS for a spatial object - in this example, a single point - and then to transform the CRS.

# Solution
When you know exactly the EPSG code or the PROJ.4 description of the CRS:
```{r}
library(sp); library(rgdal)

# Create a SpatialPoints object with a single point,
# using the SIRGASS 2000, UTM zone 23S as the CRS.
pt <- cbind(x = -23.5, y = -46.6)
crs <- CRS('+init=epsg:31983')
sp.pt <- SpatialPoints(pt, crs)

# Print the CRS.
proj4string(sp.pt)
is.projected(sp.pt)

# Transform the CRS to WGS84.
sp.pt <- spTransform(sp.pt, CRS("+init=epsg:4326"))
proj4string(sp.pt)
is.projected(sp.pt)
```

If you don't know exactly the EPSG code or the PROJ.4 description of the CRS, there are many ways to find this information.  

Suppose you have the object `sp.pt` with WGS84 as the CRS and want to tranform it to SIRGASS 2000, UTM zone 23S.
```{r}
# Make a data frame with the available CRS.
EPSG <- make_EPSG()
names(EPSG)

# Search CRS having the string "SIRGAS 2000" in their EPSG's note column.
EPSG[grep('SIRGAS *2000', EPSG$note), 1:2]

# Alternatively, a more detailed search.
pattern <- c("SIRGAS *2000", "UTM", "23S") 
matches <- Reduce('&', lapply(pattern, grepl, EPSG$note))
EPSG[matches, ]

# Transform the CRS using the EPSG code found above.
crs <- CRS('+init=epsg:31983')
sp.pt <- spTransform(sp.pt, crs)
```

Now suppose you have the object `sp.pt` with SIRGASS 2000, UTM zone 23S as the CRS and want to tranform it to WGS84. Searching for the strings "longlat" and "WGS 84" in the EPSG's note column dosen't find any CRS and searching only for "WGS 84" finds too many. As an alternative, you can search for the pattern in the EPSG's PROJ.4 column.

```{r}
pattern <- c('longlat', 'WGS *84') 
matches <- Reduce('&', lapply(pattern, grepl, EPSG$note))
EPSG[matches, 1:2]

pattern <- c('WGS *84') 
matches <- Reduce('&', lapply(pattern, grepl, EPSG$note))
# EPSG[matches, ] # Uncomment to print matches.

pattern <- c('longlat', 'WGS *84') 
matches <- Reduce('&', lapply(pattern, grepl, EPSG$prj4))
EPSG[matches, 1:2]

# Transform the CRS using the EPSG code found above.
crs <- CRS('+init=epsg:4326')
sp.pt <- spTransform(sp.pt, crs)
```

# Discussion
When a spatial object is created, the CRS must be defined. Knowing the exact EPSG code or the PROJ.4 description, the the CRS can be defined using the `CRS` function. For example, to set the CRS as WGS84, to equivalent options are `crs <- CRS('+init=epsg:2346')` and `crs <- CRS('+proj=longlat +datum=WGS84 +no_defs')`. The CRS can also be set as `NA`.  

If neigther the exact EPSG code nor the PROJ.4 description are known exactly, the CRS can be searched in a EPSG list of CRS, available in the rgdal package. The list can be read in a `data.frame` using the `make_EPSG()` function. The `data.frame` has three columns, the first has the EPSG code, the second a note and the third the PROJ.4 description. A common approach is to search a pattern in the note column. For example, to search for the pattern "SIRGAS 2000", one option is `EPSG[grep('SIRGAS 2000'), ]`. If the pattern of interest is "SIRGAS", followed by 0 or more white spaces and ending in "2000", the search can be done using `EPSG[grep('SIRGAS *2000', EPSG$note), ]`. Beacuse the search is case sensitive the following option can be used when not sure about the case
`EPSG[grep('SIRGAS *2000', EPSG$note, ignore.case = T), ]`. Sometimes, searching in the note column dosen't return a useful result but you can try using the `prj4` column. Anyway, when one or more CRS is returned, the code or the PROJ.4 description (`prj4` column) might be used to set or transform the CRS of a spatial object. The more general the pattern, the higher the probability of matching many CRS. One way to narrow the search is to look for more than one pattern in the column of interest. This is the rationale behind the code: `pattern <- c("SIRGAS *2000", "UTM", "23S")` `matches <- Reduce('&', lapply(pattern, grepl, EPSG$note))`. Here, successful matches are given by entries in the note column, containing the patterns "SIRGAS *2000", "UTM" and "23S".